Creating the ``r params$package_name`` R package

### 2025-08-23 create-FSHybridPLS.Rmd
replacer test passed

```{r}
testthat::test_that("inprod.predictor_hybrid returns correct vector output for broadcasting and other cases", {
  suppressPackageStartupMessages(library(fda))

  basis <- create.bspline.basis(c(0, 1), 5)
  make_fd <- function(val, n_sample) {
    fd(coef = matrix(val, 5, n_sample), basisobj = basis)
  }
# data generation
## three observations
  fd1 <- make_fd(1, 3)
  Z1 <- matrix(c(1, 2), nrow = 3, ncol = 2, byrow = TRUE)
  x1 <- predictor_hybrid(Z1, list(fd1, fd1))
## one observation
  fd2 <- make_fd(2, 1)
  Z2 <- matrix(c(3, 4), nrow = 1)
  x2 <- predictor_hybrid(Z2, list(fd2, fd2))
## three observations
  Z3 <- matrix(c(1, 2, 3, 4, 5, 6), nrow = 3, byrow = TRUE)
  fd3 <- fd(coef = t(matrix(c(1:15), nrow = 3, byrow = TRUE)), basisobj = basis)
  x3 <- predictor_hybrid(Z3, list(fd3, fd3))  
## one observations
  Z4 <- matrix(c(5, 6), nrow = 1)
  fd4 <- make_fd(3, 1)
  x4 <- predictor_hybrid(Z4, list(fd4, fd4))

# Case 1: Self inner product (1 sample)
  out1 <- inprod.predictor_hybrid(x2)
  expected_scalar_1 <- sum(Z2^2)
  expected_functional_1 <- sum(sapply(x2$functional_list, function(fd) fda::inprod(fd, fd)))
  testthat::expect_equal(out1, expected_scalar_1 + expected_functional_1)

# Case 2: Three-sample vs. Three-sample
  out2 <- inprod.predictor_hybrid(x1, x3)
  expected_scalar_2 <- rowSums(Z1 * Z3)
  expected_functional_2 <- vapply(1:3, function(i) {
    sum(sapply(1:2, function(j) {
      fda::inprod(x1$functional_list[[j]][i], x3$functional_list[[j]][i])
    }))
  }, numeric(1))
  testthat::expect_equal(out2, expected_scalar_2 + expected_functional_2)

  # Case 3: One-sample vs. one-sample

  out3 <- inprod.predictor_hybrid(x2, x4)
  expected_scalar_3 <- sum(Z2 * Z4)
  expected_functional_3 <-2*fda::inprod(fd2, fd4)
  testthat::expect_equal(out3, as.numeric(expected_scalar_3 + expected_functional_3))

  # Case 4: Broadcasting (single vs. multi)
  out4 <- inprod.predictor_hybrid(x2, x3)
  expected_scalar_4 <- c(0,0,0)
  for (i in 1:3){
    expected_scalar_4[i] <-  sum(Z2 * Z3[i,])
    }

  expected_functional_4 <-  c(0,0,0)
  for (i in 1:3){
    expected_functional_4[i] <- 2*fda::inprod(
      fd2,
      fd(
        coef = matrix(
        c(
        (5*i+1-5):(5*i)
        ), 5, 1), #end of matrix
         basisobj = basis) #end of fd
      )# end of inprod
  }

  testthat::expect_equal(as.vector(out4), as.vector(expected_scalar_4 + expected_functional_4))

  # Case 4: Broadcasting (multi  vs. single)
  testthat::expect_equal(as.vector(inprod.predictor_hybrid( x3, x2)), as.vector(expected_scalar_4 + expected_functional_4))  
})
```

@@

@@

  #scalar part
  rho <- rho + W$Z %*% d_vec[(K * M + 1):length(d_vec)]
  return (rho)
}
```

@@

```{r}
get_nu <- function(y, rho){
            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
            return(nu)  
}
```

```{r}
LSE_ptws <- function(input, rho) {
            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
            return(nu)
}

@@

### LSE_hybrid
```{r}
LSE_hybrid <- function(W, rho, tau) {
  C_star_J_star <- matrix(NA, nrow = W$n_sample, ncol = sum(W$n_basis_list) + W$n_scalar)
  for (ii in (1 : W$n_functional)){
    cumsum_n_basis_now <- sum(W$n_basis_list[1:ii])
    n_basis_now <- W$n_basis_list[ii]
    C_star_J_star[, (cumsum_n_basis_now - n_basis_now + 1) :cumsum_n_basis_now] <-
      t(W$functional_list[[ii]]$coefs) %*% W$jacobian_list[[ii]]
  }
  C_star_J_star[ ,(sum(W$n_basis_list) + 1) : ncol(C_star_J_star)] <- W$Z
  rho_t_C_star_J_star <- t(rho) %*% C_star_J_star

@@

>>>>

@@

### replace_obs_hybrid

```{r}
#' Replace a single observation in a predictor_hybrid object
#'
#' Replaces the i-th observation of a predictor_hybrid object with a new
#' single-sample predictor_hybrid object.
#'
#' @param W A predictor_hybrid object with one or more samples.
#' @param i An integer index specifying the observation to replace.
#' @param new_W A single-sample predictor_hybrid object to use for replacement.
#'
#' @return A predictor_hybrid object with the i-th observation replaced.
#' @export
replace_obs_hybrid <- function(W, i, new_W) {
  # Input validation
  if (!inherits(W, "predictor_hybrid") || !inherits(new_W, "predictor_hybrid")) {
    stop("Both W and new_W must be of class 'predictor_hybrid'.")
  }
  if (new_W$n_sample != 1) {
    stop("new_W must be a single-sample predictor_hybrid object.")
  }
  if (i < 1 || i > W$n_sample) {
    stop(paste("Index i must be between 1 and", W$n_sample))
  }
  if (W$n_scalar != new_W$n_scalar) {
    stop("Mismatch in number of scalar predictors.")
  }
  if (W$n_functional != new_W$n_functional) {
    stop("Mismatch in number of functional predictors.")
  }

  # Check for compatible basis objects
  is_eqbasis <- getFromNamespace("is.eqbasis", "fda")
  for (j in seq_len(W$n_functional)) {
    if (!is_eqbasis(W$functional_list[[j]]$basis, new_W$functional_list[[j]]$basis)) {
      stop("Functional predictors must have the same basis objects.")
    }
  }

  # Replace the i-th observation in the scalar matrix Z
  W$Z[i, ] <- new_W$Z[1, ]

  # Replace the i-th observation in each functional predictor
  for (j in seq_along(W$functional_list)) {
    # The coefficients are stored as a matrix, with columns corresponding to samples
    W$functional_list[[j]]$coefs[, i] <- new_W$functional_list[[j]]$coefs[, 1]
  }

  # The number of samples remains the same
  return(W)
}
```

```{r}
testthat::test_that("replace_obs_hybrid correctly replaces an observation", {
  # Setup: Create a multi-sample predictor_hybrid object
  n_samples <- 5
  n_scalar <- 2
  n_functional <- 3
  n_basis <- 5 # Assuming a fixed number of basis functions for simplicity

  # Basis object
  basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis)

  # Generate sample functional data
  functional_list_initial <- lapply(1:n_functional, function(f_idx) {
    fd(matrix(rnorm(n_basis * n_samples), ncol = n_samples), basis_obj)
  })

  # Generate sample scalar data
  Z_initial <- matrix(rnorm(n_samples * n_scalar), nrow = n_samples, ncol = n_scalar)

  W_original <- predictor_hybrid(Z = Z_initial, functional_list = functional_list_initial)

  # Create a single-sample predictor_hybrid object for replacement
  new_Z_scalar <- matrix(c(100, 200), nrow = 1)
  new_functional_list_single <- lapply(1:n_functional, function(f_idx) {
    fd(matrix(c(rep(10, n_basis), rep(20, n_basis), rep(30, n_basis))[f_idx * n_basis - (n_basis - 1):0], ncol = 1), basis_obj)
  })
  new_W_single <- predictor_hybrid(Z = new_Z_scalar, functional_list = new_functional_list_single)

  # Test Case 1: Replace a middle observation (e.g., index 3)
  index_to_replace <- 3
  W_modified <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)

  # Verify scalar part
  testthat::expect_equal(W_modified$Z[index_to_replace, ], new_W_single$Z[1, ],
               info = "Scalar part at replaced index should match new_W_single$Z")
  # Verify other scalar rows are unchanged
  if (index_to_replace > 1) {
    testthat::expect_equal(W_modified$Z[1:(index_to_replace - 1), ], W_original$Z[1:(index_to_replace - 1), ],
                 info = "Scalar part before replaced index should be unchanged")
  }
  if (index_to_replace < n_samples) {
    testthat::expect_equal(W_modified$Z[(index_to_replace + 1):n_samples, ], W_original$Z[(index_to_replace + 1):n_samples, ],
                 info = "Scalar part after replaced index should be unchanged")
  }

  # Verify functional part
  for (j in seq_len(n_functional)) {
    testthat::expect_equal(coef(W_modified$functional_list[[j]])[, index_to_replace],
                 coef(new_W_single$functional_list[[j]])[, 1],
                 info = paste0("Functional predictor ", j, " at replaced index should match new_W_single"))
    # Verify other functional columns are unchanged
    if (index_to_replace > 1) {
      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, 1:(index_to_replace - 1)],
                   coef(W_original$functional_list[[j]])[, 1:(index_to_replace - 1)],
                   info = paste0("Functional predictor ", j, " before replaced index should be unchanged"))
    }
    if (index_to_replace < n_samples) {
      testthat::expect_equal(coef(W_modified$functional_list[[j]])[, (index_to_replace + 1):n_samples],
                   coef(W_original$functional_list[[j]])[, (index_to_replace + 1):n_samples],
                   info = paste0("Functional predictor ", j, " after replaced index should be unchanged"))
    }
  }

  # Test Case 2: Replacing the first observation (index 1)
  index_to_replace <- 1
  W_modified_first <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
  testthat::expect_equal(W_modified_first$Z[index_to_replace, ], new_W_single$Z[1, ])
  for (j in seq_len(n_functional)) {
    testthat::expect_equal(coef(W_modified_first$functional_list[[j]])[, index_to_replace],
                 coef(new_W_single$functional_list[[j]])[, 1])
  }

  # Test Case 3: Replacing the last observation (index n_samples)
  index_to_replace <- n_samples
  W_modified_last <- replace_obs_hybrid(W_original, index_to_replace, new_W_single)
  testthat::expect_equal(W_modified_last$Z[index_to_replace, ], new_W_single$Z[1, ])
  for (j in seq_len(n_functional)) {
    testthat::expect_equal(coef(W_modified_last$functional_list[[j]])[, index_to_replace],
                 coef(new_W_single$functional_list[[j]])[, 1])
  }

  # Test Case 4: Error handling for invalid index
  testthat::expect_error(replace_obs_hybrid(W_original, 0, new_W_single), "Index i must be between 1 and")
  testthat::expect_error(replace_obs_hybrid(W_original, n_samples + 1, new_W_single), "Index i must be between 1 and")

  # Test Case 5: Error handling for new_W with multiple samples
  multi_sample_new_W <- predictor_hybrid(Z = matrix(rnorm(2*n_scalar), nrow=2),
                                         functional_list = lapply(1:n_functional, function(f_idx) {
                                           fd(matrix(rnorm(n_basis*2), ncol = 2), basis_obj)
                                         }))
  testthat::expect_error(replace_obs_hybrid(W_original, 1, multi_sample_new_W), "new_W must be a single-sample predictor_hybrid object.")

  # Test Case 6: Error handling for mismatch in n_scalar
  mismatch_scalar_new_W <- predictor_hybrid(Z = matrix(rnorm(1*1), nrow=1),
                                            functional_list = new_functional_list_single)
  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_scalar_new_W), "Mismatch in number of scalar predictors.")

  # Test Case 7: Error handling for mismatch in n_functional
  mismatch_functional_new_W <- predictor_hybrid(Z = new_Z_scalar,
                                                functional_list = new_functional_list_single[1]) # Only one functional predictor
  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_functional_new_W), "Mismatch in number of functional predictors.")

  # Test Case 8: Error handling for mismatch in basis objects
  different_basis_obj <- create.bspline.basis(c(0, 1), nbasis = n_basis + 1) # Different basis
mismatch_basis_new_W_list <- lapply(1:n_functional, function(f_idx) {
  # Use the correct number of rows: nbasis of different_basis_obj
  fd(matrix(rnorm(different_basis_obj$nbasis), ncol = 1), different_basis_obj)
})
  mismatch_basis_new_W <- predictor_hybrid(Z = new_Z_scalar,
                                          functional_list = mismatch_basis_new_W_list)
  testthat::expect_error(replace_obs_hybrid(W_original, 1, mismatch_basis_new_W), "Functional predictors must have the same basis objects.")

})
```

@@

  #scalar part
  rho <- rho + W$Z %*% d_vec[(K * M + 1):length(d_vec)]
  return (as.vector(rho))
}
```

@@

```{r}
get_nu <- function(y, rho){
            nu <- sum(y*rho) / sum(rho*rho)
            return(nu)  
}
```

```{r}
residualize_y <- function(y, rho){
  nu <- get_nu(y, rho)
  y_next <- y - nu * rho
  return(y_next)
}
```

output of the residualize_y and rho must be orthogonal.
```{r}
#sum(residualize_y(y, rho )*rho) #should output a very small number
```

```{r}
LSE_ptws <- function(input, rho) {
  # old implementation
            rho_norm_sq <- (Matrix::norm(rho, type = "2"))^2
            nu <- as.numeric(t(rho) %*% input) / rho_norm_sq
            return(nu)
}

@@

###  predictor residualization

$$
\widetilde{W}_i^{[l+1]} 
			:= 	\widetilde{W}_i^{[l]}  - 
			\widehat{\rho}_i^{[l]}
			\hat{\delta}^{[l]},~\text{where}~
			\delta^{[l]}
			:= 
			\frac{1}{\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2}
			\sum_{i=1}^n 
			\widehat{\rho}_i^{[l]}
			\widetilde{W}_i^{[l]},
$$

```{r}
get_delta <- function(W, rho){
  delta <- scalar_mul.predictor_hybrid(subset_predictor_hybrid(W, 1), rho[1])
   for (i in 2:length(rho)) {
  delta <- add.predictor_hybrid(delta, subset_predictor_hybrid(W, i),  rho[i]) 
} 
  return(delta)
}
```

```{r}
residualize_predictor <- function(W, delta){

}
```

### LSE_hybrid

```{r}
LSE_hybrid <- function(W, rho) {
  # old implementation
  C_star_J_star <- matrix(NA, nrow = W$n_sample, ncol = sum(W$n_basis_list) + W$n_scalar)
  for (ii in (1 : W$n_functional)){
    cumsum_n_basis_now <- sum(W$n_basis_list[1:ii])
    n_basis_now <- W$n_basis_list[ii]
    C_star_J_star[, (cumsum_n_basis_now - n_basis_now + 1) :cumsum_n_basis_now] <-
      t(W$functional_list[[ii]]$coefs) %*% W$jacobian_list[[ii]]
  }
  C_star_J_star[ ,(sum(W$n_basis_list) + 1) : ncol(C_star_J_star)] <- W$Z
  rho_t_C_star_J_star <- t(rho) %*% C_star_J_star

@@

```{r}
###########################################
)

setMethod("fitted_value",
          signature(
            "predictor_hybrid",
            "vector"
          ),
####################################################
function(regcoef, pls_score) {
  for (ii in 1 : (regcoef@n_functional) ){
    regcoef@functional_list[[ii]] <- fd(
        coef = coef(regcoef@functional_list[[ii]]) %*% matrix(pls_score, nrow=1),
        basisobj = regcoef@functional_list[[ii]]$basis
      )}
  regcoef@Z <-  pls_score %*% regcoef@Z
  return(regcoef)
  }
####################################################
)
